% ============================================================
% Results + Discussion — regenerat din campaign_summary.csv (N=5)
% Generat programatic: cifrele de mai jos provin direct din CSV.
% ============================================================

\section{Results}
\label{sec:results}

Table~\ref{tab:campaign} summarizes the full campaign: two RMW
implementations $\times$ six network conditions $\times$ five repetitions,
measured on both layers (transport echo at 4096\,B payload; full SAR mission).

\begin{table}[t]
\centering
\caption{Transport and mission-level results under physical network
degradation (\texttt{tc netem}), $N{=}5$ repetitions per cell. Loss is the
end-to-end sample loss within the per-sample deadline; missions are censored
at the 170\,s budget.}
\label{tab:campaign}
\setlength{\tabcolsep}{3.6pt}
\begin{tabular}{l rrrr rrrr}
\toprule
& \multicolumn{4}{c}{CycloneDDS} & \multicolumn{4}{c}{rmw\_zenoh} \\
\cmidrule(lr){2-5}\cmidrule(lr){6-9}
Condition & p95 & loss & $t_{\mathrm{mis}}$ & compl.
          & p95 & loss & $t_{\mathrm{mis}}$ & compl. \\
          & [ms] & [\%] & [s] & & [ms] & [\%] & [s] & \\
\midrule
ideal & 1 & 0.0 & 117 & 5/5 & 2 & 0.0 & 128 & 5/5 \\
loss 5\% & 146 & 0.0 & 122 & 5/5 & 172 & 4.4 & 123 & 5/5 \\
loss 15\% & 1056 & 0.8 & 134 & 5/5 & 690 & 2.3 & 128 & 5/5 \\
loss 30\% & 2320 & 38.7 & 132 & 5/5 & 3645 & 35.4 & 164 & 1/5 \\
200\,ms $\pm$50\,ms & 490 & 1.8 & 128 & 5/5 & 477 & 0.8 & 123 & 5/5 \\
200\,ms + loss 15\% & 2523 & 34.1 & 132 & 5/5 & 4125 & 21.8 & 133 & 4/5 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Three regimes.}
Under light degradation (5\,\% loss; latency+jitter) the two middlewares are
within tens of milliseconds of each other and all missions complete. Under
moderate pure loss (15\,\%), \texttt{rmw\_zenoh} keeps the p95 tail at
690\,ms versus 1056\,ms for CycloneDDS at a small reliability cost
(2.3\,\% vs.\ 0.8\,\% samples lost). Under heavy degradation the two
philosophies separate qualitatively, not just quantitatively.

\paragraph{Two failure modes, not one winner.}
At 30\,\% loss, CycloneDDS converts packet loss into a uniform latency wall
(p95 $\approx$2.3\,s) and still completes $5/5$ missions; \texttt{rmw\_zenoh}
delivers fresher traffic on the median but sheds 35\,\% of samples and
completes only $1/5$ missions within the budget, with coverage stalling near
0.9. In the SAR-realistic combined condition (200\,ms latency $+$ 15\,\%
loss), the distribution shapes differ fundamentally
(Fig.~\ref{fig:cdf}): the majority of \texttt{rmw\_zenoh} samples arrive
faster than the CycloneDDS retransmission wall at ${\sim}2.3$\,s, but its
tail extends beyond 5\,s, total loss is lower (21.8\,\% vs.\ 34.1\,\%), and
$4/5$ missions complete versus $5/5$. Neither middleware dominates: DDS
buys mission survival with uniform delay; Zenoh buys freshness with sample
loss that, beyond a threshold, becomes mission loss.

\paragraph{Transport-to-mission compression.}
Across all conditions, transport p95 degrades by up to three orders of
magnitude relative to the ideal baseline ($\times$1885 for CycloneDDS,
$\times$2547 for \texttt{rmw\_zenoh}), while mission completion time varies
by at most 12\,\% up to the failure threshold. Swarm autonomy absorbs
transport degradation; middleware choice is therefore decisive for
teleoperation and time-critical streams, and second-order for autonomous
mission progress---an effect invisible to transport-only benchmarks.

\section{Discussion}
\label{sec:discussion}

\paragraph{Threats to validity.}
\texttt{netem} applies i.i.d.\ Bernoulli loss; real radio links lose in
bursts, which stresses retransmission-based recovery harder---our results
are thus conservative for the Zenoh comparison and optimistic for DDS.
Both endpoints share one host (loopback), eliminating clock skew at the cost
of NIC/driver effects. The constant \texttt{rmw\_zenoh} startup offset
(${\sim}11$\,s, present in the ideal condition) is attributable to
router-based session establishment, not to the data plane, and is excluded
from per-sample statistics.
